NLIVis: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-22 paper/pipeline.tex
minor changs
update layout of the paper

\section{The p-NLI System}
In this section, we describe the p-NLI system.

% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
%
Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

>>>>

\section{NLIVis Design}
In this section, we describe the design of the NLIVis system, which address the tasks described in the previous section.

\shusen{overview of the system}

% Beside looking into the internal states, understanding how each of the component of the model interact with input and output as well as with each other is the crucial for truly examine the mechanism of the model.
%
% Look at how the model work in action and interrogate relationship between different component, i.e., how the change made to one part of model affect the other pieces present, is the key to gain the full picture.

### 2018-03-22 paper/relatedWorks.tex
update layout of the paper

One of the most studied aread in model interpretability is the explanation of a given prediction.
Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
% (Limitation of the state-of-the arts)
% Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.

\noindent\textbf{Visual Interpration of Neural Networks.}
The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})
Recently, many visualization works has dedicated to the neural network model interpretability challenges.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possiblility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training procss, so they can provide design guideline to the deep neutral network architect.

>>>>

One of the most studied aread in model interpretability is the explanation of a given prediction.
Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.

% (Limitation of the state-of-the arts)
% Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.

\noindent\textbf{Visual Exploration of Neural Networks.}
The effectiveness in the exploration of complex relationships, visualization have long been adopted for interpreting neural network models (e.g., the early works such as~\cite{TzengMa2005})
Recently, many visualization works has dedicated to the neural network model interpretability challenges.
% The classification~\cite{KrausePererNg2016}
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzing classification errors in convolutional neural networks and answer the question on whether class hierarchy is learn in the network.
Liu et al.~\cite{LiuShiCao2018} explore the possiblility of understanding the training process of deep generative models.
The ActiVis~\cite{KahngAndrewsKalro2018} focus on large scale network in real world setting.
The DeepEyes~\cite{Pezzotti2018} focuses on the analyzing the training procss, so they can provide design guideline to the deep neutral network architect.
